Soundness Proof of Dynamic Shortcut

### 2020-11-26 paper/pldi21/report/javascript.tex

\section{Dynamic Shortcuts for JavaScript}\label{sec:javascript}
In this section, we introduce the core language of JavaScript that supports
first-class functions, open objects, and first-class property names, and define
sealed symbolic execution of the core language for dynamic shortcuts.
Due to the space limitation, we present the main design of the
language in this paper and refer the interested readers to a companion report~\cite{report}.

\subsection{Core Language of JavaScript}

@@

We formulate the concrete semantics of the core language.  The transition
relation between concrete states is defined with the semantics of references and
expressions using two different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
$\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level environment address.

@@

We define the semantics of the view transition for the core language.  For abstract
memories, we use the notation $\absmem[L \mapstos \absval]$ to represent the
update of multiple abstract locations in $L$ with the abstract value $\absval$.
It performs the strong update if the abstract address for an abstract location
$(\absaddr, \_) \in L$ is singleton: $\abscount(\absaddr) = \absone$.
Otherwise, it performs the weak update for the analysis soundness.  We use
the increment function $\inc: \abscountset \times \absaddrset \rightarrow
\abscountset$ of the abstract counter defined as follows:
\[
  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
    \begin{array}{ll}
      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \abszero\\
      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \absone\\
      \abscount(\absaddr) & \text{otherwise}
    \end{array}
  \right.
\]

>>>>

\section{Dynamic Shortcuts for JavaScript}\label{sec:javascript}
In this section, we introduce the core language of JavaScript that supports
first-class functions, open objects, and first-class property names, and define
sealed symbolic execution of the core language for dynamic shortcuts.

\subsection{Core Language of JavaScript}
\begin{figure*}[t]
  \centering

  \fbox{$\st \trans \st$}
  \begin{mathpar}
    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \refer = \expr\\
      \referrule{\st}{\refer}{\loc}\\
      \exprrule{\st}{\expr}{\val}\\
    }
    {
      \st = (\lab, \mem, \ctxt, \addr)
      \trans
      (\labnext(\lab), \mem[\loc \mapsto \val], \ctxt, \addr)
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \refer = \kwobj\\
      \referrule{\st}{\refer}{\loc}\\
      \addr' = \text{(a fresh object address)}
    }
    {
      \st = (\lab, \mem, \ctxt, \addr)
      \trans
      (\labnext(\lab), \mem[\loc \mapsto \addr'], \ctxt, \addr)
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
      \referrule{\st}{\refer}{\loc}\\
      \exprrule{\st}{\expr_f}{\fval{x}{\lab_b}}\\
      \exprrule{\st}{\expr_a}{\val_a}\\
      \addr' = \text{(a fresh environment address)}
    }
    {
      \st = (\lab, \mem, \ctxt, \addr)
      \trans
      (\lab_b, \mem[(\addr', x) \mapsto \val_a], \ctxt[\addr' \mapsto (\addr,
      \labnext(\lab), \loc)], \addr')
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \kwret \; \expr\\
      \exprrule{\st}{\expr}{\val}\\
      \ctxt(\addr) = (\addr', \lab', \loc)
    }
    {
      \st = (\lab, \mem, \ctxt, \addr)
      \trans
      (\lab', \mem[\loc \mapsto \val], \ctxt, \addr')
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \kwif \; \expr \; \lab'\\
      \exprrule{\st}{\expr}{\kwtrue}\\
    }
    {
      \st = (\lab, \mem, \ctxt, \addr)
      \trans
      (\lab', \mem, \ctxt, \addr)
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \kwif \; \expr \; \lab'\\
      \exprrule{\st}{\expr}{\kwfalse}\\
    }
    {
      \st = (\lab, \mem, \ctxt, \addr)
      \trans
      (\labnext(\lab), \mem, \ctxt, \addr)
    }
  \end{mathpar}

  \fbox{$\referrule{\st}{\refer}{\loc}$}
  \begin{mathpar}
    \inferrule*[width=0.48\textwidth]
    {}
    {
      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{x}{(\addr, x)}\\
    }

    \inferrule*[width=0.48\textwidth]
    {
      \exprrule{\st}{\expr_0}{\addr_0}\\
      \exprrule{\st}{\expr_1}{\val_1}\\
      \val_1 \in \strset\\
    }
    {
      \referrule{\st = (\lab, \mem, \ctxt, \addr)}{\expr_0 [ \expr_1
      ]}{(\addr_0, \val_1)}
    }
  \end{mathpar}

  \fbox{$\exprrule{\st}{\expr}{\val}$}
  \begin{mathpar}
    \inferrule*[width=0.48\textwidth]
    {}
    {
      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\pval}{\pval}
    }

    \inferrule*[width=0.48\textwidth]
    {}
    {
      \exprrule{\st = (\lab, \mem, \ctxt,
      \addr)}{\fval{x}{\lab'}}{\fval{x}{\lab'}}
    }

    \inferrule*[width=0.48\textwidth]
    {
      \referrule{\st}{\refer}{\loc}\\
      \loc \in \Dom(\mem)
    }
    {
      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}{\refer}{\mem(\loc)}
    }

    \inferrule*[width=0.48\textwidth]
    {
      \exprrule{\st}{\expr_1}{\val_1}\\
      \cdots\\
      \exprrule{\st}{\expr_n}{\val_n}
    }
    {
      \exprrule{\st = (\lab, \mem, \ctxt, \addr)}
      {\op(\expr_1, \cdots, \expr_n)}{\op(\val_1, \cdots, \val_n)}
    }
  \end{mathpar}

  \caption{The transition relation for the core language of JavaScript}
  \label{fig:core-trans-rel}
\end{figure*}

\begin{figure*}[t]
  \centering

  \fbox{$\viewtrans{\view}{\view'}: \absdom \rightarrow \absdom$}
  \begin{mathpar}
    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
      \prog(\lab) = \refer = \expr\\
      \referabssem{\refer}(\abselem) = L\\
      \exprabssem{\expr}(\abselem) = \absval
    }
    {
      \viewtrans{\lab}{\labnext(\lab)}(\abselem) =
      (\absmem[L \mapstos \absval], \absctxt, \absaddr, \abscount)
    }

    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
      \prog(\lab) = \refer = \kwobj\\
      \referabssem{\refer}(\abselem) = L\\
      \oabsaddr = \lab
    }
    {
      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = (\absmem[L \mapstos \{
      \oabsaddr \}], \absctxt, \absaddr, \inc(\abscount, \oabsaddr))
    }

    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
      \prog(\lab) = \refer = \expr_f ( \expr_a )\\
      \referabssem{\refer}(\abselem) = L\\
      \fval{x}{\lab_b} \in \exprabssem{\expr_f}(\abselem)\\
      \exprabssem{\expr_a}(\abselem) = \absval_a\\
      \eabsaddr = \lab_b\\
      \eabsctxt = \absctxt[\eabsaddr \mapsto \absctxt(\eabsaddr) \cup \{
      (\absaddr, \labnext(\lab), L) \} ]
    }
    {
      \viewtrans{\lab}{\lab_b}(\abselem) = (\absmem[(\eabsaddr, x) \mapsto
      \absval_a], \eabsctxt, \eabsaddr, \inc(\abscount, \eabsaddr))
    }

    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
      \prog(\lab) = \kwret \; \expr\\
      \exprabssem{\expr}(\abselem) = \absval\\
      (\rabsaddr, \lab', L) \in \absctxt(\absaddr)
    }
    {
      \viewtrans{\lab}{\lab'}(\abselem) = (\absmem[L \mapstos \absval],
      \absctxt, \rabsaddr, \abscount)
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \kwif \; \expr \; \lab'\\
      \kwtrue \in \exprabssem{\expr}(\abselem)
    }
    {
      \viewtrans{\lab}{\lab'}(\abselem) = \abselem
    }

    \inferrule*[width=0.48\textwidth]
    {
      \prog(\lab) = \kwif \; \expr \; \lab'\\
      \kwfalse \in \exprabssem{\expr}(\abselem)
    }
    {
      \viewtrans{\lab}{\labnext(\lab)}(\abselem) = \abselem
    }
  \end{mathpar}

  \fbox{$\referabssem{\refer}: \absdom \rightarrow \powerset{\abslocset}$}
  \begin{mathpar}
    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)
    }
    {
      \referabssem{x}(\abselem) = \{ (\absaddr, x) \}
    }

    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
      A = \exprabssem{\expr_0}(\abselem) \cap \absaddrset\\
      S = \exprabssem{\expr_1}(\abselem) \cap \strset\\
    }
    {
      \referabssem{\expr_0 [ \expr_1 ]}(\abselem) = A \times S
    }
  \end{mathpar}

  \fbox{$\exprabssem{\expr}: \absdom \rightarrow \absvalset$}
  \begin{mathpar}
    \inferrule*[width=0.48\textwidth]
    {}
    {
      \exprabssem{\pval}(\abselem) = \{ \pval \}
    }

    {}
    {
      \exprabssem{\fval{x}{\lab}}(\abselem) = \{ \fval{x}{\lab} \}
    }

    \inferrule*[width=0.48\textwidth]
    {
      \abselem = (\absmem, \absctxt, \absaddr, \abscount)\\
      \absval = \bigjoin \{ \absmem(\absloc) \mid \absloc \in
      \referabssem{\refer}(\abselem) \}
    }
    {
      \exprabssem{\refer}(\abselem) = \absval
    }

    \inferrule*[width=0.48\textwidth]
    {
      \exprabssem{\expr_1}(\abselem) = \absval_1\\
      \cdots\\
      \exprabssem{\expr_n}(\abselem) = \absval_n
    }
    {
      \exprabssem{\op(\expr_1, \cdots, \expr_n)}(\abselem) = \ops(\absval_1,
      \cdots, \absval_n)
    }
  \end{mathpar}

  \caption{The semantics of view transition for the core language of JavaScript}
  \label{fig:core-view-trans}
\end{figure*}

@@

We formulate the concrete semantics of the core language as described in
Figure~\ref{fig:core-trans-rel}.  The transition relation between concrete
states is defined with the semantics of references and expressions using two
different forms \fbox{$\referrule{\st}{\refer}{\loc}$} and
\fbox{$\exprrule{\st}{\expr}{\val}$}, respectively.  The initial states are
$\istset = \{ (\ilab, \varnothing, \epsilon, \tladdr) \}$ where $\ilab$ denotes
the initial label, $\epsilon$ empty map, and $\tladdr$ the top-level
environment address.  The function $\labnext$ returns the next label of a
given label in the current program $\prog$.

@@

We define the semantics of the view transition for the core language in
Figure~\ref{fig:core-view-trans}.  For abstract memories, we use the notation
$\absmem[L \mapstos \absval]$ to represent the update of multiple abstract
locations in $L$ with the abstract value $\absval$.  It performs the strong
update if the abstract address for an abstract location $(\absaddr, \_) \in L$
is singleton: $\abscount(\absaddr) = \absone$.  Otherwise, it performs the weak
update for the analysis soundness.  We use the increment function $\inc:
\abscountset \times \absaddrset \rightarrow \abscountset$ of the abstract
counter defined as follows:
\[
  \inc(\abscount)(\absaddr_0) = \lambda \absaddr \in \absaddrset. \; \left\{
    \begin{array}{ll}
      \absone & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \abszero\\
      \absmany & \text{if} \; \absaddr = \absaddr_0 \wedge
      \abscount(\absaddr_0) = \absone\\
      \abscount(\absaddr) & \text{otherwise}
    \end{array}
  \right.
\]

### 2020-11-26 paper/pldi21/report/report.tex
Minor changed in report
Changed the formal definition
Modified definition
Remove duplicated package from report.tex

\documentclass[11pt]{article}
\usepackage[a4paper,left=20mm,right=20mm,top=30mm,bottom=25mm]{geometry}

\usepackage{mathtools}
\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathpartir}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{stmaryrd}
\usepackage{tikz}
\usepackage{dirtree}
\usepackage{multicol}
\usepackage{array}
\usepackage{galois}
\usepackage{amsthm}

\usetikzlibrary{arrows}
\tikzset{
  treenode/.style = {align=center, inner sep=0pt, text centered},
  arn_n/.style = {treenode, circle, black, draw=black, text width=1.5em},
}

@@

\input{macros}

\title{Dynamic Shortcut Soundness Proof}

\author{Dongjun Youn$^*$ \and Jihyeok Park$^*$ \and Sukyoung Ryu$^*$}

\date{$^*$KAIST, South Korea}
\maketitle

\input{proof}

\end{document}

>>>>

\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

\usepackage{float}
%\usepackage{amssymb}
\usepackage{amsmath,amsfonts}
\usepackage[ruled, vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{galois}
\usepackage{mathpartir}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{stmaryrd}

\EnableBpAbbreviations

\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

\input{../macros}

@@

\title
[Accelerating JavaScript Static Analysis via Dynamic Shortcuts]
{Accelerating JavaScript Static Analysis\\ via Dynamic Shortcuts}

\author{Joonyoung Park}
\affiliation{%
  \institution{Korea Advanced Institute of Science and Technology}
  \state{Daejeon}
  \country{South Korea}
}
\email{gmb55@kaist.ac.kr}

\author{Jihyeok Park}
\affiliation{%
  \institution{Korea Advanced Institute of Science and Technology}
  \state{Daejeon}
  \country{South Korea}
}
\email{jhpark0223@kaist.ac.kr}

\author{Dongjun Youn}
\affiliation{%
  \institution{Korea Advanced Institute of Science and Technology}
  \state{Daejeon}
  \country{South Korea}
}
\email{f52985@kaist.ac.kr}

\author{Sukyoung Ryu}
\affiliation{%
  \institution{Korea Advanced Institute of Science and Technology}
  \state{Daejeon}
  \country{South Korea}
}
\email{sryu.cs@kaist.ac.kr}

\renewcommand{\shortauthors}{Park and Park, et al.}

\input{../abstract}

\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{JavaScript, static analysis, dynamic analysis, dynamic shortcut, sealed symbolic execution}

\maketitle

\input{intro}
\input{../motivation}
\input{../shortcut}
\input{ds}
\input{javascript}
\input{../implementation}
\input{eval}
\input{../eval-opaque}
\input{../related}
\input{../conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{../ref}

\end{document}
\endinput
